%-------------------------------------------------------------------------------
%	SECTION TITLE
%-----------------------------------------------------------------------------
\vspace{-3mm}
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-1mm}
\begin{cventries}

%---------------------------------------------------------
\cventry
{\textbf{Senior Software Engineer}} % Job title
{\href{https://www.zluri.com/}{Zluri}} % Organization
{Apr. 2025 - Present} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Revamped notification service with minimal impacts, reducing peak-hour message delivery latency from \textbf{2 hours} to under \textbf{1 minute}.}
    \item {Performed cross-functional bug bashes and refactored critical legacy modules, resulting in a \textbf{33\%} drop in on-call tickets.}
    \item {Improved system reliability and maintainability by implementing robust \textbf{service-level disaster recovery} and optimizing performance through query enhancements.}
    \item {Ideated \& implemented a development workflow for the organization using feature environments, automated testing etc. for multiple services and background jobs resulting in higher engineering productivity and faster project delivery}
    \item {\textbf{Mentored junior engineers and interns} through onboarding, code reviews, and project execution.}
    \item {Tools and Technologies used: TypeScript, NodeJS, Golang, Kafka, MongoDB, Postgres, AWS, CI/CD.}
\end{cvitems}}
%---------------------------------------------------------
\vspace{1mm}
\cventry
{\textbf{Software Development Engineer}} % Job title
{} % Organization
{Nov. 2023 - Mar. 2025} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Lead the development of a greenfield project, \href{https://www.linkedin.com/posts/zluri_ditch-the-chaos-of-complex-access-reviews-activity-7209563170468691970-MeRA}{\textbf{Multilevel Access Reviews}}. Delivered with exceptional code quality and a extensible design making agile future development possible and work \textbf{at scale}, resulting in a robust new revenue stream.}
    \item {Achieved a \textbf{65\% reduction in the time} required for raising and approving application requests by engineering \href{https://zluri-1.wistia.com/medias/svw7jw37f1}{\underline{Slack integrations}} for the same.}
    \item {\textbf{Improved operational excellence} by promptly tackling on-call issues and service/API failures.}
    \item {Collaborated with Product Managers, Design, and Customer Support teams to proactively deliver features and address customer pain points.}
    \item {Led the efforts within my team to \textbf{migrate our database} from MongoDB to Postgres, ensuring data integrity and relational consistency. Contributed to the organization's broader migration strategy.}
    \item {Leveraged \textbf{AWS DMS} for efficient data migration and developed \textbf{DBT scripts} to format and structure data accurately in Postgres tables. Built the Data Access Layer and migrated APIs and background jobs to integrate seamlessly with Postgres.}
    \item {Tools and Technologies used: Javascript, TypeScript, NodeJS, MongoDB, Postgres, \href{https://docs.bullmq.io/}{Bull MQ}, \href{https://argoproj.github.io/workflows/}{Argo}, AWS S3, AWS DMS, DBT, \href{https://sentry.io/welcome/}{Sentry}, \href{https://www.datadoghq.com/}{Datadog}.}
\end{cvitems}}
%---------------------------------------------------------
\vspace{3mm}
\cventry
{\textbf{Software Development Engineer}} % Job title
{\href{https://www.captainfresh.in/}{Captain Fresh}} % Organization
{Jun. 2022 - Oct. 2023} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Spearheaded the \textbf{remodeling of the finance module}. Worked with Product Managers to develop technical specifications. Designed and built the \textbf{backend service} to process all \textbf{vendor/customer payments}, and incorporated credit/debit knock-off behavior in a \textbf{scalable} fashion.}
    \item {Achieved a \textbf{4x performance boost} in payment processes compared to the previous Zoho ERP setup. }
    \item {Implemented \textbf{two-way sync} between the previous ERP and the new Finance service in a \textbf{master-slave setup} for transactional integrity.}
    \item {\textbf{Contributed vital UI components} to the Finance Module, \textbf{accelerating product development} while emphasizing collective efficiency.}
    \item {Tools and Technologies used: Java, SpringBoot, Golang, \href{https://github.com/ironman19933/service-framework}{Service Framework}, Hibernate, PostgreSQL, AWS S3, AWS SQS, AWS SNS, ReactJS.}
\end{cvitems}}
%---------------------------------------------------------
\vspace{1mm}
\cventry
{\textbf{Backend Intern}} % Job title
{} % Organization
{Jan. 2022 - May 2022} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Built the \textbf{first production ready version of in-house Finance Backend module} from scratch to handle customer and vendor transactions.}
    \item {Designed and implemented transaction and ledger behaviour, integrated Razorpay payment schemes to handle order processing and refunds.}
    \item {\textbf{Engineered an expense module} which accepted company wide expenses and validated them based upon expense category and type.}
    \item {Tools and Technologies used: Java, SpringBoot, Hibernate, JHipster, PostgreSQL, Golang, Iris, MongoDB.}
\end{cvitems}}
%---------------------------------------------------------
\vspace{3mm}
\cventry
{\textbf{Software Intern}} % Job title
{\href{https://www.deshaw.com/}{D.E. Shaw \& Co.}}
{May. 2021 - July. 2021} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed and deployed an in-house toolset from scratch to aggregate, display and update datasets informations used by Finance wing.}
    \item {\textbf{Enhanced overall productivity by 200\%} by reducing the dependence of the financial stakeholders over Ops team and eliminating slow e-mail based communications.}
    \item {Tools and Technologies used: ReactJS, Redux, Python.}
    % \item {Acquired a Pre Placement Offer (PPO).}
\end{cvitems}}
%---------------------------------------------------------
\end{cventries}